---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(readr)
library(here)
library(streamgraph)
library(janitor)
library(readxl)
```

```{r data}
#Read in data
p0621 <- read_csv(here("data", "shared_data", "dashboard data", "sample_p0621.csv"))
```


Police stops and frisks in New York City {.sidebar}
=========
This dashboard provides data of the **Stop and Frisk Program in New York City**. Stop and frisk is the practice of temporarily detaining, questioning, and searching suspects on the street for weapons and suspicious materials. Since its introduction in the early 1980s, the program has been criticized as increasing racial profiling and police-initiated violence.

This dashboard used data of the stop and frisk program to explore the relationship between a suspect's race and their likelihood of being stopped and frisked by a police officers.

The original data come from the New York City Police Department website in separate annual files. I combined those files to obtain a complete set of data covering the **2006 - 2021** period. This combined data set contains over four million rows, which made it very difficult to use. I obtained a randomized sample of 160,000 rows and used this sample to complete this dashboard.

Stop frisk by race
========


Row {data-height=650}
-----------------------------------------------------------------------

### Number and distribution of police stops by subject race {data-width=10}
text holder

```{r, eval=TRUE, echo=FALSE, include=FALSE}

#Create plot data
p0621_racedata <- p0621 %>%
  filter(race!= "Unknown") %>%
  group_by(race, year) %>%
  summarize(count_stop=n(),
            count_frisk=sum(frisked =="Y"),
            count_search = sum(searched =="Y"),
            percent_frisk = count_frisk/count_stop*100,
            percent_search = count_search/count_stop*100) %>%
  mutate(race = fct_relevel(race, "White", 
                        "White Hispanic", 
                        "Black", 
                        "Black Hispanic",
                        "Asian/Pacific Islander",
                        "American Indian/ Alaskan Native",
                        "Others",
                        "Unknown"))

#Assign color

colors1 <- c('#FFA600',"#ff764a", "#ef5675", '#bc5090', '#7a5195', '#374c80', '#003f5c', '#000000')

my_scale1 <- scale_fill_manual(name=p0621_racedata$race, values=colors1)

```

```{r, eval=TRUE, echo=FALSE, include=TRUE}
#Percent of police stops by subject race

streamgraph(p0621_racedata, key="race", 
                            value = "count_stop", 
                            date = "year",
                            offset="expand") %>%
  sg_fill_manual(values=colors1) %>%
  sg_axis_x(tick_interval = 1) %>%
  sg_legend(show=TRUE, label= "Racial and ethnic group")

#Problems with this graph:
##The x axis and filter option shows in the viewer but not the exported document
##I have not figured out how to add axis titles to this graph and arrange the races in the order and colors I want.
```


### Reference 2020 census data {data-width=5}

```{r census}
census2020 <- read_excel(here("data", "shared_data", "census_data", "2020censusNY.xlsx")) %>%
              clean_names() %>%
              mutate(race_ethnicity = fct_relevel(race_ethnicity,
                                                  "American Indian and Alaska Native alone",
                                                  "Asian/Pacific Islander",
                                                  "Black or African American alone",
                                                  "Hispanic or Latino",
                                                  "Others",
                                                  "White alone"))

my_scale2 <- scale_fill_manual(name=census2020$race_ethnicity, values=colors1)

ggplot(census2020, aes(x=year, y=percent)) +
  geom_col(aes(fill=race_ethnicity)) +
  my_scale2 +
  labs(fill="Racial and ethnic groups") +
  theme_minimal() +
  theme(plot.background=element_blank(),
        panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x= element_blank())

#No idea why 2020 shows up as 3 different years.
```



Row
-------

### Likelihood of subject being frisked once stopped, by subject race
text holder

```{r, fig.width= 15}
p0621_racedata %>%
  group_by(race) %>%
  summarize(percent_frisk_avg=mean(percent_frisk), na.rm=TRUE) %>%
  ggplot(aes(race, percent_frisk_avg)) +
  geom_col(aes(fill=race)) +
  my_scale1 + 
  labs(y= "Percentage of subject being frisked, averaged by year") +
  theme(plot.background=element_blank(),
        panel.grid = element_blank(),
        axis.title.x = element_blank()) +
  coord_flip()

?theme

```



Stop frisk and temperature {data-orientation=rows}
=======

Row
----------

### Chart 1

```{r}


```


### Chart 2

```{r}


```

Row
---------------------
### Chart 3

```{r}

```

